### 2017-09-06 Graduate - Introduction to Analysis I/Assignment 2/2_Homework20170831.tex
update assignment 1'
update
add problem 4.a, 4.b

\textbf{Solution:}
\begin{proof}
\textbf{(a)} \\[2pt]
$$
\begin{aligned}
\sum_{n\ne m}\frac{1}{m^2-n^2} &= -\frac{1}{2m}\sum_{n\ne m}\left(\frac{1}{n-m}-\frac{1}{n+m} \right)\\
&=-\frac{1}{2m}(-\frac{1}{m-1}-\frac{1}{m+1}-\cdots-1-\frac{1}{2m-1}\\
&\quad + 1-\frac{1}{2m+1}+\cdots+\frac{1}{m}-\frac{1}{3m}\\
&\quad + \frac{1}{m+1}-\frac{1}{3m+1}+\cdots+\frac{1}{2m}-\frac{1}{4m}+\cdots) \\
&= -\frac{1}{2m}\left(\lim_{n\to\infty}(-\sum_{i=-m}^{m}\frac{1}{n+i}) + \frac{1}{m} + \frac{1}{2m}\right) \\
&= -\frac{3}{4m}.
\end{aligned}
$$
\\
\textbf{(b)} 
According to (a),
$$
\sum_{n=0}^{\infty}u_{mn} = -\frac{3}{4m^2}+\frac{1}{m^2} = \frac{1}{4m^2}, ~\sum_{m=0}^{\infty}u_{mn} = -\frac{1}{4n^2}.
$$
Thus
$$
\sum_{m=0}^{\infty}\left(\sum_{n=0}^{\infty} u_{mn}\right) = -\sum_{n=0}^{\infty}\left(\sum_{m=0}^{\infty} u_{mn}\right) = \sum_{n=1}^{\infty}\frac{1}{4n^2}\ne 0.
$$
\\
\textbf{(c)}
\end{proof}
\bigskip

@@

>>>>

\textbf{Solution:}
\begin{proof}
\textbf{(a)} \\[2pt]
$$
\begin{aligned}
\sum_{n\ne m}\frac{1}{m^2-n^2} &= -\frac{1}{2m}\sum_{n\ne m}\left(\frac{1}{n-m}-\frac{1}{n+m} \right)\\
&=-\frac{1}{2m}(-\frac{1}{m-1}-\frac{1}{m+1}-\cdots-1-\frac{1}{2m-1}\\
&\quad + 1-\frac{1}{2m+1}+\cdots+\frac{1}{m}-\frac{1}{3m}\\
&\quad + \frac{1}{m+1}-\frac{1}{3m+1}+\cdots+\frac{1}{2m}-\frac{1}{4m}+\cdots) \\
&= -\frac{1}{2m}\left(\lim_{n\to\infty}(-\sum_{i=-m}^{m}\frac{1}{n+i}) + \frac{1}{m} + \frac{1}{2m}\right) \\
&= -\frac{3}{4m}.
\end{aligned}
$$
\\
\textbf{(b)} 
According to (a),
$$
\sum_{n=0}^{\infty}u_{mn} = -\frac{3}{4m^2}+\frac{1}{m^2} = \frac{1}{4m^2}, ~\sum_{m=0}^{\infty}u_{mn} = -\frac{1}{4n^2}.
$$
Thus
$$
\sum_{m=0}^{\infty}\left(\sum_{n=0}^{\infty} u_{mn}\right) = -\sum_{n=0}^{\infty}\left(\sum_{m=0}^{\infty} u_{mn}\right) = \sum_{n=1}^{\infty}\frac{1}{4n^2}\ne 0.
$$
\\
\textbf{(c)}
The computation of (b) has the same principle as (c)$\to$(b) in prob. 2.
\end{proof}
\bigskip

@@

\textbf{Solution:}
\begin{proof}
\textbf{(a):}\\[2pt]
\textbf{Sufficiency:}
For $\forall A\subset \mathbb{R}$, first we have $m^*(A) \le m^*(A\cap E) + m^*(A\cap E^c)$. So we only need to show that $m^*(A) \ge m^*(A\cap E) + m^*(A\cap E^c)$. According to assumption, $m^*(A\cap E) + m^*(A\cap E^c) \le m^*(A\cap O)+m^*(A\cap F^c) < m^*(A\cap O)+m^*(A\cap O^c)+\epsilon$. Since the open set $O$ is measurable, we have $m^*(A\cap )+m^*(A\cap O^c) = m^*(O)$. Thus by the arbitrariness of $\epsilon$, we know that $m^*(A) = m^*(A\cap E)+m^*(A\cap E^c)$. \\[2pt]

\textbf{Necessity:} We first show that $\forall \epsilon > 0$, we can find an open set $O\supset E$, s.t. $m^*(O\setminus E) < \epsilon$. \\[2pt]
First, if $m^*(E) <\infty$. Then according to definition of outer measure, $\forall\epsilon > 0$, there is an open cover $\{O_i\}$ of $E$, s.t. 
$$
\sum_{i}m^*(O_i) < m^*(E)+\epsilon.
$$
Let $O = \bigcup_{i}O_i$, then $m^*(O) < m^*(E)+\epsilon$, and $O$ is an open set. Thus 
$$
m^*(O\setminus E) = m^*(E)-m^*(E\cap O) = m^*(O)-m^*(E) < \epsilon.
$$
If $m^*(E) = \infty$, define $E_{n} = \{x\in E:|x|\le n\}$. Then $E_n$ is measurable with finite outer measure, the argument above shows that there is an open set $O_k\supset E_k$, s.t.
$$
m^*(O_k\setminus E_k) < \frac{\epsilon}{2^k}.
$$
Then $O = \bigcup_{k} O_k$ is an open set that contains $E$, and 
$$
m^*(O\setminus E) = m^*\left(\bigcup_{k}O_k\setminus E\right)\le\sum_{k}m^*(O_k\setminus E)\le\sum_{k}m^*(O_k\setminus E_k)<\epsilon.
$$
So there is an open set $O\supset E$, s.t. $m^*(O\setminus E) < \frac{\epsilon}{2}$. Meanwhile, since $E^c$ is measurable, there is an open set $G\supset E^c$, s.t. $m^*(G\setminus E^c)<\frac{\epsilon}{2}$. Thus we have a closed set $F = G^c$, and $O\supset E\supset F$,
$$
m^*(O\setminus F) \le m^*(O\setminus E)+m^*(E\setminus F) = m^*(O\setminus E)+m^*(G\setminus E^c) < \epsilon.
$$
\\[2pt]
\textbf{(b):}
From (a) we know that $\forall \epsilon > 0$, there exists an open set $G$ and a closed set $F$, s.t. $G\supset E\supset F$. So 
$$
m(G\setminus E) \le m(G\setminus F) < \epsilon, ~m(E\setminus F) \le m(G\setminus F) < \epsilon.
$$
Thus we can construct two series of sets $\{G_k\}$ and $\{F_k\}$:
$$
G_k\supset E\supset F_k, ~m(G_k\setminus E) < \frac{\epsilon}{2^k}, ~m(E\setminus F_k) < \frac{\epsilon}{2^k}.
$$
Thus $G = \bigcap G_k$ is a $G_\delta$ set, and $F = \bigcup F_k$ is a $F_\sigma$ set, and
$$
m(G) - m^*(E) \le m(G\setminus E) < \frac{\epsilon}{2^n}, ~m^*(E)-m(F)\le m(E\setminus F) < \frac{\epsilon}{2^n}.
$$
Let $n\to\infty$, we have $m^*(E) = m(G) = m(F)$. \\[2pt]
\textbf{(c):}

\end{proof}
\bigskip
